Get population and temperature data

### 2021-12-03 getdata.Rmd
add Introduction and fix bug
modifications ...

@@

```{r gettemp}
source("R/tempdat.R")
umetemp <- tempdat("ume", c(1895, 1950))
bjurtemp <- tempdat("bjur", c(1895, 1950))
##stentemp <- tempdat("~/Forskning/Data/sten_temp.csv", c(1899, 1952))
saveRDS(umetemp, file = "data/umetemp.rds")
saveRDS(bjurtemp, file = "data/bjurtemp.rds")
```

@@

```{r makecommunal}
##source("R/make_comm.R")
lagg <- 3 / 365  ## NOTE!!
##lagg <- 0
## Ume:
bume <- births[births$subreg == "ume", ]
bume <- make.communal(bume, umetemp["heat"], start = 1895, period = 1/52, lag = lagg)
bume <- bume[bume$enter < bume$exit, ]
bume <- make.communal(bume, umetemp["cold"], start = 1895, period = 1 / 52, lag = lagg)
bume <- bume[bume$enter < bume$exit, ]
bume <- make.communal(bume, umetemp["week"], start = 1895, period = 1 / 52, lag = lagg)
bume <- bume[bume$enter < bume$exit, ]
### Ske:
bskel <- births[births$subreg == "bjur", ]
bskel <- make.communal(bskel, bjurtemp["heat"], start = 1895, period = 1/52, lag = lagg)
bskel <- bskel[bskel$enter < bskel$exit, ]
bskel <- make.communal(bskel, bjurtemp["cold"], start = 1895, period = 1 / 52, lag = lagg)
bskel <- bskel[bskel$enter < bskel$exit, ]
bskel <- make.communal(bskel, bjurtemp["week"], start = 1895, period = 1 / 52, lag = lagg)
bskel <- bskel[bskel$enter < bskel$exit, ]
##bsten <- births[births$subreg == "sten", ]
##bsten <- make_comm(bsten, stentemp, start = 1899, period = 1/52, lag = lagg)
bume$region <- "ume"
bskel$region <- "ske"
infdat <- rbind(bume, bskel)
infdat <- infdat[order(infdat$id, infdat$enter), c("region", "id", "sex", "enter", "exit", "event", 
                                                   "birthdate", "socStatus", "hisclass", "illeg",
                                                   "parity", "heat", "cold", "week")]
saveRDS(infdat, file = "data/infdat.rds")
```

>>>>

# Introduction

Note thet we now have corrected the mistake with zero-length intervals.

@@

```{r gettemp}
source("R/tempdat.R")
temp_start <- 1894
temp_end <- 1951
t_ivl <- c(temp_start, temp_end)
umetemp <- tempdat("ume", t_ivl) # Changed interval!
bjurtemp <- tempdat("bjur", t_ivl) # Ditto!
##stentemp <- tempdat("~/Forskning/Data/sten_temp.csv", c(1899, 1952))
saveRDS(umetemp, file = "data/umetemp.rds")
saveRDS(bjurtemp, file = "data/bjurtemp.rds")
```

@@

```{r makecommunal}
##source("R/make_comm.R")
lagg <- 3 / 365  ## NOTE!!
##lagg <- 0
## Ume:
bume <- births[births$subreg == "ume", ]
bume <- make.communal(bume, umetemp["heat"], start = temp_start, period = 1/52, lag = lagg)
bume <- bume[bume$enter < bume$exit, ]
bume <- make.communal(bume, umetemp["cold"], start = temp_start, period = 1 / 52, lag = lagg)
bume <- bume[bume$enter < bume$exit, ]
bume <- make.communal(bume, umetemp["week"], start = temp_start, period = 1 / 52, lag = lagg)
bume <- bume[bume$enter < bume$exit, ]
### Ske:
bskel <- births[births$subreg == "bjur", ]
bskel <- make.communal(bskel, bjurtemp["heat"], start = temp_start, period = 1/52, lag = lagg)
bskel <- bskel[bskel$enter < bskel$exit, ]
bskel <- make.communal(bskel, bjurtemp["cold"], start = temp_start, period = 1 / 52, lag = lagg)
bskel <- bskel[bskel$enter < bskel$exit, ]
bskel <- make.communal(bskel, bjurtemp["week"], start = temp_start, period = 1 / 52, lag = lagg)
bskel <- bskel[bskel$enter < bskel$exit, ]
##bsten <- births[births$subreg == "sten", ]
##bsten <- make_comm(bsten, stentemp, start = 1899, period = 1/52, lag = lagg)
bume$region <- "ume"
bskel$region <- "ske"
infdat <- rbind(bume, bskel)
infdat <- infdat[order(infdat$id, infdat$enter), c("region", "id", "sex", "enter", "exit", "event", 
                                                   "birthdate", "socStatus", "hisclass", "illeg",
                                                   "parity", "heat", "cold", "week")]
saveRDS(infdat, file = "data/infdat.rds")
```
